How to compute the fusion product of MV cycles in type A

### 2021-02-19 draft.tex
delete old stuff

    \acom{Different letter fine by me. Maybe $\UU$? And, I guess we do not need $\AA$ but it is a nice letter to have. It is also good to distinguish the $\CC$ over which $R,K$ is defined and the $\AA$ over which $\Grbd$ is defined?}
\end{itemize}

\subsection{Old stuff}
\jcom{I'm going to delete everything below here in this section, if that is ok with you.}

% New (?) definitions among these are as follows.
% 
%The [family of] slices [with $s$-fibre?]
%\begin{equation}
%    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
%\end{equation}

>>>>

    \acom{Maybe $\UU$ for a different letter? And, I guess we do not need $\AA$ but it is a nice letter to have around. It also serves to distinguish the $\CC$ over which $R,K$ are defined from the $\AA$ over which $\Grbd$ is defined?}
\end{itemize}

\subsection{Old stuff}
\jcom{I'm going to delete everything below here in this section, if that is ok with you.}
\acom{Yup!}
% New (?) definitions among these are as follows.
% 
%The [family of] slices [with $s$-fibre?]
%\begin{equation}
%    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
%\end{equation}
